Graph Generators: State of the Art and Open Challenges

### 2019-12-18 reviewresponse.tex

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/)
%
% BASIC INSTRUCTIONS:
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,11pt]{reviewresponse}

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{subfig}
\usepackage{epstopdf}

% 2. Complete the paper data
\newcommand{\myAuthors}{{Angela Bonifati, Irena Holoubova, Arnau Part-Perez and Sherif Sakr} }
\newcommand{\myEmail}{holubova@ksi.mff.cuni.cz}
\newcommand{\myTitle}{Response Letter to Review Comments}
\newcommand{\myShortTitle}{CSUR-2019-0568}
\newcommand{\myJournal}{Journal: ACM Computing Surveys}
\newcommand{\manuTitle}{Manuscript Title: \textbf{Graph Generators: State of the Art and Open Challenges}}
\newcommand{\manuId}{Manuscript ID: \textbf{CSUR-2019-0568}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[linktoc=all]{hyperref}
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=black!70!green,          % color of internal links
citecolor=black!70!green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=black!70!green           % color of external links
}

\begin{document}

\thispagestyle{plain}

\begin{center}
 {\LARGE\myTitle} \vspace{0.5cm} \\
  {\large\myJournal} \vspace{0.5cm} \\
  \large\manuTitle \vspace{0.5cm} \\
  \manuId \vspace{0.5cm} \\
 \myAuthors \\
 \url{\myEmail} \vspace{1cm} \\
\end{center}

%\tableofcontents

\begin{abstract}
The authors would like to thank the reviewers for their detailed, useful and constructive comments to improve the manuscript. Please find below our responses to the comments which have been included in the attached revised version for our manuscript.
\end{abstract}

\section{Reviewer 1 (Minor Revision)}

\rcomment{
I do not think it is necessary to modify the review to include lengthy discussions of graph generators that are primarily used for null models or molecule design. However, the introduction should more clearly delineate the scope of the review as being focused on graph generators that are designed for benchmarking.
}

\textbf{Response}

Thanks for the comment. We have specified benchmarking as a main context for our surveyed graph generators.

\section{Reviewer 2 (Accept)}

The reviewer has been satisfied with the manuscript and did not have comments to address.

\section{Reviewer 3 (Minor Revision)}

\rcomment{
Authors say MapReduce-based BTER algorithm can generate large graphs in a reasonable amount of time. I find such a sentence too vague to be of any substance. What is a large graph? What is a reasonable amount of time? }

\textbf{Response}

.....

\rcomment{List of Typos}
\textbf{Response}
Thanks for the listed typos. We have addressed them and made an additional proof-reading round of the manuscript.

% Uncomment in case references are needed
%\bibliographystyle{apalike}
%\bibliography{response}

\end{document}

### 2019-12-18 main.tex
Response Letter

In this survey, we provide a detailed overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

>>>>

In this survey, we provide a detailed overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks and benchmarking context. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:
